Texture mapping 3D planar models of indoor environments with noisy camera poses

### 2013-01-10 spie/_region_.tex
new paper draft

\message{ !name(paper.tex) !offset(674) }
\subsection{Future stuff}
For the sake of simplicity, - cases where multiple whatever are few,
but for true generality, should go to 3d adjustments

\begin{figure*}
  \centering
  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}}
  ~~~~~~~~
  \centering
  \subfloat[][]{\includegraphics[width=3in]{finalceilings.jpg}}

  \centering 
  \subfloat[][]{\includegraphics[height=2in, width=3in]{floorcropped.jpg}}
  ~~~~~~~~
  \centering
  \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
  \caption{Examples of our final texture mapping output for (a) walls,
    (b) ceilings, (c) an entire floor, (d) a full model.}
  \label{fig:results}
\end{figure*}

@@

\message{ !name(paper.tex) !offset(672) }

>>>>

\message{ !name(paper.tex) !offset(690) }
\section{Results and Conclusions}
\label{sec:resultsAndConclusions}
Examples of ceilings and floors textured with the tile caching
approach, and walls textured with the shortest path approach, are
displayed in Figure \ref{fig:results}. High resolution texture
comparisons, as well as a walkthrough of a fully textured 3D model are
available in the accompanying video to this paper.

As mentioned earlier, our approach is quite efficient. The top wall in
Figure \ref{fig:results}(a) was generated with 7543 $\times$ 776
pixels, and spans a 40-meter long wall. Given 41000 input images, a
2.8GHz consumer-grade laptop takes approximately a minute to pick 36
candidate images, followed by another minute to perform both image alignment and the shortest
path texturing method, with the majority of computation time spent
calculating SIFT matches within the SiftGPU framework. While not quite
real-time visualization, the process is capable of generating quick
updates after changes in various parameters or modifications to input
data.

In this paper, we have developed two approaches to texture map models
with noisy camera localization data. We are able to refine image
locations based on geometry references and feature matching, and
robustly handle outliers. The tile-based mapping approach can be used
to texture both simple rectangular walls as well as complex floor and
ceiling geometry. We also developed a shortest path texturing method
that produces seamless textures on planes where multiple head-on
images are available. Both of these approaches are highly modular, and
easily tunable for different environments and acquisition systems.

\begin{figure}
  \centering
  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}} ~~~~~~~~
  \centering
  \subfloat[][]{\includegraphics[width=3in]{finalceilings.jpg}}

  \centering \subfloat[][]{
    \includegraphics[height=2in, width=3in]{floorcropped.jpg} ~~~~~~~~
    \includegraphics[width=3in]{pier15floor.jpg}
  }

  \centering{
    \includegraphics[width=1.9in]{fullmodel.png}
    \includegraphics[width=1.9in]{threestoryfull2.png}
    \includegraphics[width=1.9in]{pier15.png} \\
    \includegraphics[width=6in]{threestoryfull.png}
  }

  \centering \subfloat[][]{ }
  \caption{Examples of our final texture mapping output for (a) walls,
    (b) ceilings, (c) floors, (d) full models.}
  \label{fig:results}
\end{figure}

@@

\message{ !name(paper.tex) !offset(688) }
